---
title: "UNICEF"
subtitle: "Child Dependency Quatro Report - 2023"
author: "Shakthi Rishi R V - 22264249 - DCU"
date: last-modified
date-format: "DD-MM-YYYY"
description: "This Dashboard compares the Child Dependency Ratio with Gross National Income, Population and GDP per Capita."
title-block-banner: "#27445C"
format: 
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Report Flow
    toc-depth: 3
css: styles.css  
execute:
  echo: false
  warning: false
  message: false
---

## Executive Summary
 All the data used in developing this report is from **UNICEF**.

### Key Highlights
 

- There is a **Correlation** between the Child Dependency Ratio and Population, Gross National Income & GDP per Capita. 

- As the **population grows**, the **child dependency ratio reduces** which clearly indicates that there are more adults now than before to take care of children in a macro view. 

- The **child dependency ratio decreases** with **increase in Gross National Income, GDP per Capita and Population**. Now, it helps to understand that the individual Income of people also plays a crucial factor alongside population.

- The **more the income of people** across population growth, the **lesser the child dependency** is. This also means that the adult individuals are now **more financially stable** and capable of taking responsibility for more children than before, which reduces the child dependency significantly.

- Precisely, countries in *Africa* tend to have **Higher** Child Dependency comparitively, the possible reasons could be their:

  **- Low GDP per Capita** 
  
  **- Slow Economic Growth of the Nation**
  
  **- Lesser Gross National Income**
  


Check out the Tableau version of this report - [Click Here](https://public.tableau.com/views/ChildDependencyDashboard/Dshboard2?:language=en-GB&publish=yes&:display_count=n&:origin=viz_share_link) 

## The Child Dependency Story
```{r}
#| label: setup
#| include: false
library(ggplot2)
library(magrittr)
library(dplyr)
library("tidyverse") # load dplyr, ggplot2, stringr, etc.
library("sf") # working with geographic simple features in R
library("rnaturalearth") # World map data from Natural Earth
library("countrycode") # get ISO code from country names
library("ggrepel") # "ggplot2" extension for overlapping text labels
library(readr)
unicef_metadata <- read_csv("~/Documents/DCU MiM Course Work/Data Analytics/mt5000importantdataandinstructionstableauassignmen/unicef_metadata.csv")
unicef_indicator_2 <- read_csv("~/Documents/DCU MiM Course Work/Data Analytics/mt5000importantdataandinstructionstableauassignmen/unicef_indicator_2.csv")
metadata_from_2009<- unicef_metadata %>% 
  filter(year>2008)
world <- ne_countries(scale = "small", returnclass = "sf")
countries_obs_value<- world %>%
   select(geometry, name, iso_a3) %>%
     left_join(unicef_indicator_2, by = c("iso_a3" = "alpha_3_code")) %>%
     filter(time_period==2023) %>%
     filter(sex=="Total")
countries_obs_2023 <- unicef_indicator_2  %>%
      filter(time_period==2023) %>%
      filter(sex=="Total")
Countries_over80 <- countries_obs_2023 %>%
     filter(obs_value>80)
Countires_under20 <- countries_obs_2023 %>%
     filter(obs_value<20)
```

#### Child Dependency across the World
```{r}
world %>%
     filter(admin != "Antarctica") %>%
     st_transform(crs = "+proj=robin") %>%
     ggplot() +
     geom_sf(color = "darkgrey") +
     geom_sf(data = countries_obs_value, aes(fill = obs_value)) +
     theme_minimal() +
     theme(plot.title = element_text(face = "bold"),
           axis.text.x = element_blank(),
           legend.position = "bottom") +
     labs(title = "World Map - Child Dependency 2023",
          subtitle = "Graphical Representation using Simple Features Library (SF)",
          x = NULL, y = NULL,
          caption = "Source: Unicef")
```
- As per the above World Map, it is noted that most countries in *Africa* tend to have **High** Child Dependency and countries like  *South Korea, Japan, Singapore, UAE, Taiwan etc.* have **Low** Child Dependency. 




- Countries in *Africa* tend to have **Higher** Child dependency ratios Comparitively (from Below Bar Chart).


```{r}
 ggplot(Countries_over80, aes(x = obs_value , y = country )) + 
  geom_col(aes(fill=country), width = 0.5) +  
  theme_light()+
  theme(axis.text.x = element_text(angle=65, vjust=0.6), legend.position = "bottom") +
    labs(title="Countries with High Child Dependency 2023", 
          subtitle="Bar Chart - Country x Child Dependency (>80)", 
          caption="Source: Unicef",x="Child Dependency Ratio", y="Country") +
  scale_fill_discrete(name = "Countries") +
  theme(legend.title = element_text(colour="Black", size=10, 
                                      face="bold"))
  
```


- Countries like *Singapore, Japan, UAE, Italy, Hong Kong* etc. tend to have **Lower** Child dependency ratios comparitively (from Bottom 5 Countries Bar Chart Below), the possible reasons could be their High GDP per Capita, High economic growth and High gross national income.



```{r}
ggplot(Countires_under20, aes(x = obs_value , y = country)) + 
     geom_col(aes(fill=country), width = 0.5)    +
    theme_light()+
 theme(axis.text.x = element_text(angle=65, vjust=0.6),legend.position = "bottom") +
      labs(title="Countries with Low Child Dependency 2023",
         subtitle="Bar Chart - Country x Child Dependency (<20)", 
           caption="Source: Unicef",x="Child Dependency Ratio", y="Country")+
  scale_fill_discrete(name = "Countries")+ 
  theme(legend.title = element_text(colour="Black", size=10, 
                                      face="bold"))
```



```{r}
ggplot(metadata_from_2009, aes(x=year)) + 
               geom_line(aes(y=`GNI (current US$)`),color="limegreen") + 
              labs(title="Time Series Chart of Gross National Income", 
                                             subtitle="GNI x Year from 2009", 
                                             caption="Source: Unicef Metadata", 
                                              y="Gross National Income", x="Year")+ 
        scale_y_continuous(labels = scales::label_number_si()) +
              theme_light()
```
**Insights:**

- GNI steadily **increases** over the years. 
- Child Dependency reduces with Increase in Gross National Income. 


```{r}
metadata_from_2009 %>% 
        group_by(year)%>% 
     summarise(s_pop=sum(`Population, total`)) %>%
     ggplot(aes(year,s_pop), color="seagreen4")+
     geom_point()+
     geom_smooth(method = 'lm')+
     scale_y_continuous(labels = scales::label_number_si())+
         labs(title="World Population Scatter Plot with Regression Line", 
                         subtitle="Population x Year from 2009", 
                         caption="Source: Unicef Metadata",x="Year", y="Population")+
  theme_light()

```
**Insights:**

- Population **increases** rapidly over the years. 


#### GDP Per Capita
- Sum of gross value added by all resident producers in the economy plus any product taxes (less subsidies) not included in the valuation of output, divided by mid-year population.
```{r}
ggplot(metadata_from_2009, aes(x=year)) + 
                    geom_point(aes(y=`GDP per capita (constant 2015 US$)`),color="violetred") +
                    labs(title="GDP Per Capita Scatterplot",                                                                    subtitle="GDP Per Capita x Year from 2009",                                                                   caption="Source: Unicef Metadata", 
                             y="GDP Per Capita", x="Year") + 
                       scale_y_continuous(labels = scales::label_number_si()) +
                              theme_light()
```
**Insights:**

- As **GDP Per Capita Increases** over the years and **Child Dependency Reduces**.



